Meta RL analyses

### 2019-02-13 meta_RL_analyses.Rmd
Basic + meta mapping card results in the paper

reward_d = reward_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho))
```

@@

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ named_run_type)
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3)
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout",
                               "basic_random_holdout_longer",# "basic_only_one", "basic_only_one_ho",
                               "language", "language_drop_03", "language_drop_05", "language_noncompositional"
                               ), num_runs, "new_meta_true_losses")

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)))
```

@@

```{r}
summary_plot(meta_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ named_run_type)

ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3)
```

>>>>

reward_d = reward_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho),
         is_new_game = factor(is_new_game, labels=c("Trained", "Held out")))
```

@@

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ named_run_type) + 
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout",
                               "basic_random_holdout_longer"# "basic_only_one", "basic_only_one_ho",
                               #"language", "language_drop_03", "language_drop_05", "language_noncompositional"
                               ), num_runs, "new_meta_true_losses")

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)),
         is_new = factor(is_new, labels=c("Trained", "Held out")))
```

@@

```{r}
summary_plot(meta_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3.5)
ggsave("writing/figures/meta_mapping.png", width=5, height=3.5)
```

### 2019-02-13 writing/embedded_meta_learning.tex
Basic + meta mapping card results in the paper

\subsubsection{Results}
\textbf{Basic meta learning:} First, we show that the  \par
\textbf{Meta mapping (task $\rightarrow$ task):} \par
\textbf{Basic language (language $\rightarrow$ task):} \par
\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} \par

>>>>

\subsubsection{Results}
\begin{figure}

\end{figure}
\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out task from a few examples in Fig. \ref{cards_basic_results}. We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``Losers'' variations of the ``straight flush'' game. In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case. It is worth noting that the sample complexity in terms of number of tasks trained on is not that high, even training on 20 tasks leads to good generalization. Furthermore, starting from this ``guess'' at the correct strategy, the system can rapidly learn to achieve optimal performance ($< 20$ epochs, figure TODO). \par
\begin{figure}
\centering
\includegraphics[width=0.66\textwidth]{figures/basic_meta_learning.png}
\caption{Basic meta-learning successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.}
\label{cards_basic_results}
\end{figure}
\textbf{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior. For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training. In Fig. \ref{cards_meta_map_results}) we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it. This task is more difficult than simply learning to play a held out game from examples, because the system will actually receive no examples of the target game (when it is held out). Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so it is encouraging to see rewards that are substantially above 0. Again, given training the system can learn how to achieve this mapping perfectly. \par
\begin{figure}
\centering
\includegraphics[width=0.66\textwidth]{figures/meta_mapping.png}
\caption{The system generalizes to meta-mapping new tasks. The system is trained to do the three meta-mappings shown here, and is able to generalize to tasks it has not been trained to map. For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants. When given a game it has not mapped in this way, it is able to map it to the losers variation. This plot shows the reward produced by taking the mapped embedding and playing the targeted game.}
\label{cards_meta_map_results}
\end{figure}
\textbf{Basic language (language $\rightarrow$ task):} \par
\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} \par
